Towards semantic-rich word embeddings

### 2019-03-27 paper/main.tex
Minor fixes

\subsection{Baseline}
\label{sec:exp_baseline}
As the baseline for optimization experiments, we check how keyword and context embeddings perform without any extra optimizations (\ref{sec:exp_baseline_model}).
We evaluate the performance of the baseline model with different context lengths, to see how it affects top-k accuracies (Fig. \ref{fig:baseline}).

\begin{figure}
    \centering
    \caption{Top-k accuracies of the baseline model with different context lengths.}
    \label{fig:baseline}
    \includegraphics[scale=0.7]{res/baseline_context_top_acc.png}
\end{figure}

>>>>

\subsection{Baseline}
\label{sec:exp_baseline}
As the baseline for optimization experiments, we check how keyword and context embeddings perform without any extra optimizations (\ref{sec:baseline_model}).
We evaluate the performance of the baseline model with different context lengths, to see how it affects top-k accuracies (Fig. \ref{fig:baseline}).

\begin{figure}
    \centering
    \caption{Top-k accuracies of the baseline model with different context lengths.}
    \label{fig:baseline}
    \includegraphics[scale=0.5]{res/baseline_context_top_acc.png}
\end{figure}
